Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-03-08 apples_and_oranges.qmd
Trying to workout how to extract stats for subgroup analyses

@@

# Convert the results to a dataframe
result_df <- data.frame(
   subgroup = met_perc_women$subgroup.name,
   TE = met_perc_women$TE.random,
  seTE = met_perc_women$seTE.random,
  lower = met_perc_women$lower.random,
  upper = met_perc_women$upper.random
)

@@

Description of results X.

@@

### Number of sites
## This data lives in this spreadsheet for psy trials, we need to merge it in

@@

# ### do ALL studies using percentage at baseline
# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
# 
# 
# #turn sds to sec
# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(all_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get CDRS studies
# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
# 
# #turn sds to sec
# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get HAM-D studies
# hamd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
# 
# 
# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
#                                                           %in% hamd_study_ids,]
# 
# hamd_studies_for_baseline_metareg <- list_hamd_study # 
# 
# #turn sds to sec
# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
# 
# 
# # Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels
# 
# # We will do in two ways
# # First by excluding studies with a diagnostic classification of "sub"
# 
# clin_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
# 
# clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% clin_study_ids)
# 
# #turn sds to sec
# clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(clin_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
# results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# # Now lets include only studies with classification of "mdd"
# 
# mdd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id
# 
# mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% mdd_study_ids)
# 
# mdd_studies_baseline_metareg %>% 
#   filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
#   summarise(n = n())
# 
# #turn sds to sec
# mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(mdd_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
# results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# # Now CBT + all med studies
# 
# cbt_meds_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
# 
# cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% cbt_meds_study_ids) %>% 
#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
# 
# #turn sds to sec
# cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(cbt_meds_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
# results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# # Look at the diagnostics of included studies 
# 
# filtered_data <- df_appl_v_orange %>%
#   filter(psy_or_med == 1) %>% 
#   filter(new_study_id %in% cbt_meds_study_ids) %>%
#   distinct(new_study_id, .keep_all = TRUE)
# 
# summary_result <- filtered_data %>%
#   group_by(diagnosis) %>%
#   summarise(count = n())
# 
# # Now the CBT + med studies, filtering out the subclinical studies
# 
# clin_cbt_meds_study_ids <-
#   df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id
# 
# clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
# 
# #turn sds to sec
# clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
# results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
#                                                          model_1, condition)

@@

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample
# D) the no WL or CAU sample
# E) the CDRS only sample
# F) percentage variables

@@

# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
 # grab the ids for no waitlist and cau
no_wl_cau_ids <- df_appl_v_orange %>%
  filter(!(control_type %in% c("wl", "cau"))) %>%
  pull(new_study_id)

list_no_wl_cau <- lapply(list_df_simulated, function(df) {
  df %>%
    filter(new_study_id %in% no_wl_cau_ids) %>%
    filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
})

# count studies 
no_wl_cau_studies <- df_long_for_metan %>% 
  filter(new_study_id %in% no_wl_cau_ids) %>%
  filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
study_count_no_wl_cau_study <- count_studies(no_wl_cau_studies)
# CB checked, looks good!

# apply the metareg function to the list of no wl or cau
list_model_1_no_wl_cau <- run_metaregression(list_no_wl_cau , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_no_wl_cau <- aggregate_model_results(list_model_1_no_wl_cau, condition)
aggregate_results_no_wl_cau <- cbind(aggregate_results_no_wl_cau, condition)

# now use the function to extract the coefficients
means_no_wl_cau <-  lapply(list_model_1_no_wl_cau, extract_coefficients_func)

# run the mean function for no wl
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
coef_and_se_means_no_wl_cau <- calculate_mean_coefs_ses(means_no_wl_cau, condition)
coef_and_se_means_no_wl_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_cau))

coef_and_se_means_no_wl_cau$n <- study_count_no_wl_cau_study[study_count_no_wl_cau_study$is_missing 
                                                     ==FALSE,]$n

# here are all three of them OVERALL, CBT and WL together. We may want to display them together. 
# df_all_coefficients <- cbind(df_mean_coefs_from_sim, coef_and_se_means_cbt_fluox_esc_study,coef_and_se_means_no_wl)

@@

# test <- df_appl_v_orange %>%
#   filter(psy_or_med == 1) %>%
#   distinct(new_study_id, .keep_all = TRUE)
# 
# summary_test <- test %>%
#   group_by(diagnosis) %>%
#   summarise(count = n())

@@

# G. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------

# the first thing to do is to create a new dataset with the percentage cohen's d

list_df_simulated_percentage <- list_df_simulated

for(i in 1: length(list_df_simulated_percentage)){

  list_df_simulated_percentage[[i]]$cohens_d <- 
            (list_df_simulated_percentage[[i]]$perc_post_mean - list_df_simulated_percentage[[i]]$perc_baseline_mean)/
    ((list_df_simulated_percentage[[i]]$perc_post_sd + list_df_simulated_percentage[[i]]$perc_baseline_sd)/2)

list_df_simulated_percentage[[1]]

list_df_simulated[[1]]

# specify model
model_1 <- as.formula(~ four_level_var )

# run metareg function 
# here you can use the simulated results directly
list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_perc <-  aggregate_model_results(list_model_1_meta_reg_perc, condition)
aggregate_results_perc <- cbind(aggregate_results_perc, condition)

# extract SMDs from the  list
means_perc <-  lapply(list_model_1_meta_reg_perc, extract_coefficients_func)

# calculate mean SMDs and ses
df_mean_coefs_perc <- calculate_mean_coefs_ses(means_perc, condition)
df_mean_coefs_perc <- data.frame(cbind(condition,df_mean_coefs_perc))

# add the ns
df_mean_coefs_perc <- data.frame(cbind(df_mean_coefs_perc, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))

##### now for the baseline controlled variable
# specify model
model_2 <- as.formula(~ four_level_var + perc_baseline_mean )

# run metareg function 
# here you can use the simulated results directly
list_model_2_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_2)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_perc_mod_2 <-  aggregate_model_results(list_model_2_meta_reg_perc, condition)
aggregate_results_perc_mod_2 <- cbind(aggregate_results_perc_mod_2, condition)

# extract SMDs from the  list
means_perc_mod_2 <-  lapply(list_model_2_meta_reg_perc, extract_coefficients_func)

# calculate mean SMDs and ses
df_mean_coefs_perc_mod_2 <- calculate_mean_coefs_ses(means_perc_mod_2, condition)
df_mean_coefs_perc_mod_2 <- data.frame(cbind(condition,df_mean_coefs_perc_mod_2))

# add the ns
df_mean_coefs_perc_mod_2 <- data.frame(cbind(df_mean_coefs_perc_mod_2, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))

# Plots  -----------------------
# 
# #define groups
# df_long_for_metan <- df_long_for_metan %>%
#   mutate(
#     group = case_when(
#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
#       TRUE ~ NA_character_  
#     )
#   )

@@

>>>>

# Define function for baseline metaanalyses  ----------------------------------------------

# subgroup_df <- data.frame(psy_or_med = c(0, 1))
# 
# result <- list()
# name_vec <- character()
# 
# # Loop over rows in the subgroup_df
# for (i in 1:nrow(subgroup_df)) {
#   
#   # Call the metagen function for each row
#   result[[i]] <- metagen(
#     TE = percent_women,
#     seTE = percent_women_std_error,
#     studlab = new_study_id,
#     data = df_for_gender_metan[df_for_gender_metan$psy_or_med == subgroup_df$psy_or_med[i], ],
#     sm = "",
#     fixed = FALSE,
#     random = TRUE,
#     method.tau = "REML",
#     hakn = TRUE,
#     title = paste("Subgroup:", subgroup_df$psy_or_med[i])
#   )
#   
#   name_vec[i] = paste("Subgroup:", subgroup_df$psy_or_med[i])
# }
# 
# # Now result contains the metagen results for each subgroup
# # name_vec contains names for each subgroup
# 
# ## Function to extrac the key results for graphing and tabulating.
# 
# extract_stats <- function(result) {
#  
#   # get the summary table with results
#   statistics <- summary(result)
#   
#   # Extract specific stats
#   extracted_stats <- c(
#     k_study = statistics$k.study,
#     TE_random = statistics$TE.random,
#     lower_random = statistics$lower.random,
#     upper_random = statistics$upper.random,
#     pval = statistics$pval.random,
#     tau2 = statistics$tau2,
#     lower_tau2 = statistics$lower.tau2,
#     upper_tau2 = statistics$upper.tau2
#   )
#   
#   return(extracted_stats)
# }
# 
# extract_stats(result[[1]])
# extract_stats(result[[2]])
# 
# # create a dataframe with the results
# statistics_indiv_metan <- lapply(result, extract_stats) 
# statistics_indiv_metan <- data.frame(do.call("rbind", statistics_indiv_metan))
# statistics_indiv_metan$condition <- name_vec

@@

# met_perc_women_overall <- metagen(TE = percent_women,
#                            seTE = percent_women_std_error,
#                            studlab = new_study_id,
#                            data = df_for_gender_metan,
#                            sm = "",
#                            fixed = FALSE,
#                            random = TRUE,
#                            method.tau = "REML",
#                            hakn = TRUE,
#                            title = "percentage women across studies")
# 
# subgroup_metan <-update.meta(met_perc_women_overall  , 
#                               subgroup = df_for_gender_metan$psy_or_med, subgroup.name = "treatment modality",
#                               tau.common = FALSE)

# Use the summary function with the 'byvar' argument
summary_met_perc_women <- summary(met_perc_women, byvar = "psy_or_med")

# Extract specific statistics for each subgroup
subgroup_names <- summary_met_perc_women$subgroup.name
TE_random <- summary_met_perc_women$TE.random
seTE_random <- summary_met_perc_women$seTE.random
lower_random <- summary_met_perc_women$lower.random
upper_random <- summary_met_perc_women$upper.random
pval <- summary_met_perc_women$pval.random
tau2 <- summary_met_perc_women$tau2
lower_tau2 <- summary_met_perc_women$lower.tau2
upper_tau2 <- summary_met_perc_women$upper.tau2

# Create a data frame to store the results
result_df <- data.frame(
  subgroup = subgroup_names,
  TE_random = TE_random,
  seTE_random = seTE_random,
  lower_random = lower_random,
  upper_random = upper_random,
  pval = pval,
  tau2 = tau2,
  lower_tau2 = lower_tau2,
  upper_tau2 = upper_tau2
)

@@

Description of results X + table.

@@

### Number of sites
Write results, tabulate.

## This data lives in this spreadsheet for psy trials, we need to merge it in

@@

# ### do ALL studies using percentage at baseline
# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
# 
# 
# #turn sds to sec
# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(all_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get CDRS studies
# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
# 
# #turn sds to sec
# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get HAM-D studies
# hamd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
# 
# 
# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
#                                                           %in% hamd_study_ids,]
# 
# hamd_studies_for_baseline_metareg <- list_hamd_study # 
# 
# #turn sds to sec
# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
# 
#

# # Look at the diagnostics of included studies 
# 
# filtered_data <- df_appl_v_orange %>%
#   filter(psy_or_med == 1) %>% 
#   filter(new_study_id %in% cbt_meds_study_ids) %>%
#   distinct(new_study_id, .keep_all = TRUE)
# 
# summary_result <- filtered_data %>%
#   group_by(diagnosis) %>%
#   summarise(count = n())
#

@@

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample
# E) the CDRS only sample (**Argyris** do we still want this?)
# F) Clinical Levels Depression

@@

@@

@@

@@

```{r}
# Plots  -----------------------
# 
# #define groups
# df_long_for_metan <- df_long_for_metan %>%
#   mutate(
#     group = case_when(
#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
#       TRUE ~ NA_character_  
#     )
#   )
